---
title: "Banovic Lab"
output: 
  html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Thank you for visiting Banovic Labs Website: a research lab in the Small Animal Medicine and Surgery (SAMS) department of the University of Georgia (UGA).

Our lab focuses on dermatological studies for **many** species, from murine to equine, feline, canine, and including human. 

Frequently dermatologically, and often immunologically, diseases present with phenotypical _and_ cellular molecular similarity. This is especially true concerning mammals, as they  have evolved similarly over time and will have a higher rate of conserved molecular pathways. Translational medicine between species allows multiple animals to benefit from further understanding of certain diseases.

This lab examines dermatological diseases and the immunological pathways stimulating inflammation, itch, and especially: the core molecular pathways of the specific disease in the immune system that allows symptomatic flare ups and issues to become chronic in their nature. We do this using a number of techniques that we discuss on the laboratory techniques page.

Our website is currently under construction; please excuse the mess. ~Last updated 8/30/2019~


```{r welcome}
knitr::opts_chunk$set(echo = FALSE)
```
