---
title: "Banovic Lab"
output: 
  html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
png(filename="UGA_itchyBulldog.png")
```

Thank you for visiting Banovic Labs Website: a research lab in the [Small Animal Medicine and Surgery (SAMS) department of the University of Georgia (UGA)](https://vet.uga.edu/education/academic-departments/small-animal-medicine-and-surgery/).

Our lab focuses on dermatological studies for **many** species, from murine to equine, feline, canine, and including human. 

Frequently dermatologically (and often immunologically), diseases present with phenotypical _and_ cellular molecular similarity. As mammals share a high level of conserved molecular pathways, translational medicine allows multiple species to benefit from further understanding of certain diseases, from lupus to atopic dermatitis.

Specifically, this lab examines dermatological diseases and the immunological pathways utilized to stimulate inflammation, itch, and other symptoms. Especially, we try to understand the core molecular pathways allowing symptomatic flare ups to become chronic in their nature and define the disease. These pathways can be treated with more targeted therapies when they are better understood, allowing greater relief of symptoms. We do this using a number of techniques, discussed on the laboratory techniques page.

Our website is currently under construction; please excuse the mess. ~Last updated 8/30/2019~


```{r welcome}
knitr::opts_chunk$set(echo = FALSE)
```
